---
title: "Homework 1"
author: "Lauren Huang"
date: "2022-09-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Machine Learning Main Ideas

Please answer the following questions. Be sure that your solutions are clearly marked and that your document is neatly formatted. You don’t have to rephrase everything in your own words, but if you quote directly, you should cite whatever materials you use (this can be as simple as “from the lecture/page # of book”).

### Question 1: Define supervised and unsupervised learning. What are the difference(s) between them?
Answer: Supervised learning is when a model can estimate or predict an output because the input data has the correct labels to tell how accurate the model is during training/testing.In unsupervised learning, we are not given "the correct labels", or the supervised output. We have no way to tell the numeric range of accuracy of the model, we can only infer the relationships between data.(learned from lecture 1)


### Question 2: Explain the difference between a regression model and a classification model, specifically in the context of machine learning.
Answer: Regression is used when we predict outcomes that are quantitative and continuous. (ex. price, blood pressure) In contrast, classification is used to predict outcomes that are qualitative or discrete/categorical. (ex. survived/died, spam/not spam) (examples from lecture 1)


### Question 3: Name two commonly used metrics for regression ML problems. Name two commonly used metrics for classification ML problems.
Answer: 2 common metrics for regression ML problems are training mean squared error(MSE) and testing mean square error.
2 common metrics for classification ML problems are Bayes classifier and K-nearest neighbors.


### Question 4: As discussed, statistical models can be used for different purposes. These purposes can generally be classified into the following three categories. Provide a brief description of each.
a. Descriptive models: best for a visual representation or emphasis of a data trend. (from lecture 1)

b. Inferential models: helps us distinguish the features/predictors that are most significant to the outcome. This method tests features against one another, and also helps clarify the relationship between features.

b. Predictive models: goal is to predict outcome with the minimum reducible error (from lecture 1), often uses past behavior to help predict the future.


### Question 5: Predictive models are frequently used in machine learning, and they can usually be described as either mechanistic or empirically-driven. Answer the following questions.
a. Define mechanistic. Define empirically-driven. How do these model types differ? How are they similar?

Answer: Mechanistic refers to theory and how we assume data follows a certain form. Empirically-driven means that we do not make any assumptions about how data is. When using a mechanistic, we may never match the true unknown value of the data. With empirically-driven, we require a many more observations than we would working with a mechanistic model. An empirically-driven model is more flexible by default than a mechanistic model, though we can add parameters to a mechanistic model to help it become more flexible. One similarity between the two models is to be conscious of over fitting, where the model is too sensitive and picks up on noise that does not directly follow a trend. (ideas from lecture 1)

b. In general, is a mechanistic or empirically-driven model easier to understand? Explain your choice.

Answer: *TYPE ANSWER HERE*

c. Describe how the bias-variance trade off is related to the use of mechanistic or empirically-driven models.

Answer: Mean square error (MSE) involves the components of variance and bias. With more flexible models, variance increases and bias decreases. On the other hand, when variance decreases, bias increases. One commonality between both mechanistic and empirically-driven models is the aspect of flexibility. Empirically-driven models are generally flexible by default; While mechanistic models may not be very flexible at first, we can add parameters to make it more flexible. Because of the flexibility in these models, it might not be difficult to eliminate bias. The challenge that concerns both types of models is the bias-variance trade-off. It can be easy to achieve either low variance or low bias, but our goal to find a method that gives both low variance and low bias. 


### Question 6: A political candidate’s campaign has collected some detailed voter history data from their constituents. The campaign is interested in two questions. Classify each question as either predictive or inferential. Explain your reasoning for each.
a. Given a voter’s profile/data, how likely is it that they will vote in favor of the candidate?

Answer: Predictive, because voter profile/data can be considered our input, and one characteristic of predictive models is using past knowledge/data to help predict the outcome (not focused on hypothesis tests).

b. How would a voter’s likelihood of support for the candidate change if they had personal contact with the candidate?

Answer: Inferential, because this situation has not happened yet, it is a theory. Inferential models aim to test theories and decipher a possible relationship between predictors (ex. personal contact with candidate) and the outcome (who the voter votes for).


## Exploratory Data Analysis

This section will ask you to complete several exercises. For this homework assignment, we’ll be working with the mpg data set that is loaded when you load the tidyverse. Make sure you load the tidyverse and any other packages you need.

Exploratory data analysis (or EDA) is not based on a specific set of rules or formulas. It is more of a state of curiosity about data. It’s an iterative process of: generating questions about data, visualize and transform your data as necessary to get answers, use what you learned to generate more questions
A couple questions are always useful when you start out. These are “what variation occurs within the variables,” and “what covariation occurs between the variables.”

You should use the tidyverse and ggplot2 for these exercises.
```{r, echo=T, eval=T}
library(tidyverse)
library(ggplot2)
```

### Exercise 1: We are interested in highway miles per gallon, or the hwy variable. Create a histogram of this variable. Describe what you see/learn.

```{r, echo=T, eval=T}
# Histogram
ggplot(mpg, aes(x=hwy)) + geom_histogram()
```

Answer: There are a large amount of cars that can run approximately 26 highway miles per gallon. The next largest category would be cars that can run about 15 highway miles per gallon. Most cars call into the category of less than 37-38 highway miles per gallon, there are very few cars that can run over 40 highway miles per gallon.


### Exercise 2: Create a scatter plot. Put hwy on the x-axis and cty on the y-axis. Describe what you notice. Is there a relationship between hwy and cty? What does this mean?

```{r, echo=T, eval=T}
# Scatter plot
ggplot(mpg, aes(x=hwy, y=cty)) + geom_point()
```

Answer: There seems to be a positive correlation between hwy and cty. This means that hwy and cty will both change in the same direction. (ex. increase together, decrease together)


### Exercise 3: Make a bar plot of manufacturer. Flip it so that the manufacturers are on the y-axis. Order the bars by height. Which manufacturer produced the most cars? Which produced the least?

```{r, echo=T, eval=T}
# Check the numbers of each type of car from manufacturers
#sum(mpg$manufacturer == "dodge")
#sum(mpg$manufacturer == "toyota")
#sum(mpg$manufacturer == "land rover")
#sum(mpg$manufacturer == "mercury")
#sum(mpg$manufacturer == "lincoln")

# Bar plot
bar_plot <- ggplot(data=mpg, aes(x=reorder(manufacturer, manufacturer, function(manufacturer)-length(manufacturer)))) +
  geom_bar()

# Flip the Bar plot so manufacturer is on the y-axis
bar_plot + coord_flip()
```

Answer: From the bar chart, Dodge produced the most cars and Lincoln produced the least cars.


### Exercise 4: Make a box plot of hwy, grouped by cyl. Do you see a pattern? If so, what?

```{r, echo=T, eval=T}
# Box plot
box_plot <- ggplot(mpg, aes(group=cyl, x=hwy, y=cyl)) + 
  geom_boxplot()

box_plot
```

Answer: The general pattern I see is that a cyl and hwy are negatively correlated (lower number of cylinders corresponds to greater number of highway miles per gallon).


### Exercise 5: Use the corrplot package to make a lower triangle correlation matrix of the mpg dataset. (Hint: You can find information on the package here.) Which variables are positively or negatively correlated with which others? Do these relationships make sense to you? Are there any that surprise you?

```{r, echo=T, eval=T}
#install.packages("corrplot")
library(corrplot)

# mpg dataset, select numeric variables
cars <- mpg %>% select(displ, cyl, cty, hwy)
# put through correlation function
car_corr <- cor(cars)
head(car_corr)
# plot lower triangular correlation matrix
corrplot(car_corr, type = "lower", method = 'number')
```

Answer: cty and hwy are positively correlated, just as we expected from Exercise 2. hwy and cyl are negatively correlated, just as we expected from Exercise 4. The other correlations I have not graphed/tested in previous exercises, but based on their correlation, they seem to all make sense. For example, cty and cyl have negative correlation, cty and displ have negative correlation, so it makes sense that cyl and displ have positive correlation.
